A Survey of Quantitative Descriptions of Molecular Structure

### 2012-05-18 paper.tex
Added a bit of text on online APIs

>>>>

There are also web interfaces wrapping descriptor calculation tools
and some of these interfaces have a programmable feature. For example,
AMBIT2 implement the OpenTox API providing a REST-like interface
to descriptor calculation~\cite{Jeliazkova2011,Hardy2010} (see Figure~\ref{fig:tools}). Another
online application programming interface for descriptor calculation
is provided by the SADI platform, which, like AMBIT2, uses semantic
web technologies for descriptor calculation~\cite{Chepelev2011b}.
